---
title: "p8105_hw5_dr3168"
author: "Daniela Rochez"
date: "11/15/2021"
output: github_document
editor_options: 
  chunk_output_type: console
---

```{r}
library(tidyverse)
library(rvest)
set.seed(1)
```


Problem 2

#Loading the Excel Files and creating a function for reading them
```{r}
all_files=
           list.files(path= "./long data",
                      recursive=T,
                      pattern=".csv",
                      full.names=T)

```

```{r}
reading_data= function(x){
  read=read_csv(x)
  read}
```

#Applying the function using map to create a data frame
```{r}
subject_df= 
  purrr::map_dfr(all_files,reading_data)
```
#Adding new variables for subjects, relocating them to beggining of the data frame, and changing some variables to factors
```{r}
new_df=
  subject_df %>% 
  mutate(arm= all_files) %>% 
  mutate(subject_id= all_files) %>% 
  relocate(arm) %>% 
  relocate(subject_id) %>% 
  mutate(arm= as.factor(arm))
```
#Tidying the data and separatinf variables
```{r}
tidy_data=
  pivot_longer(
    new_df, 
    week_1:week_8,
    names_to = "week", 
    names_prefix = "week_",
    values_to = "observations") %>% 
  mutate(week=as.numeric(week)) %>% 
  mutate(arm= str_sub(arm, 13,15)) %>% 
  mutate(subject_id= str_sub(subject_id, 13,18)) 
  
view(tidy_data)
```

#Creating a spaghetti plot
```{r}
tidy_data %>% 
  ggplot(
    aes(x = week,y = observations,
        color=subject_id))+
  geom_line()
```

#It seems like the experimental has higher observations than the control arm.



Problem 3