---
title: "p8105_hw5_dr3168"
author: "Daniela Rochez"
date: "11/15/2021"
output: github_document
editor_options: 
  chunk_output_type: console
---

```{r}
library(tidyverse)
library(rvest)
```

Problem 1
#Loading CSV file
```{r}
homicide_df= 
  read_csv("homicide-data.csv", 
           na= c("", "Unknown")) %>% 
  mutate(city_state= str_c(city, state),
         resolution= case_when(
           disposition== 
             "Closed without arrest" ~ "unsolved",
           disposition== 
             "Open/No arrest" ~ "unsolved",
           disposition== 
             "Closed by arrest" ~ "solved")) %>% 
  relocate(city_state) %>% 
  filter(city_state != "TulsaAL") %>% 
  view()
```
#Focus on Baltimore
```{r}
baltimore_df= 
  homicide_df %>% 
  filter(city_state== "BaltimoreMD")

baltimore_summary=
  baltimore_df %>%
  summarize(unsolved= 
              sum(resolution== "unsolved"),
            n=n())

baltimore_test=
  prop.test(
  x= baltimore_summary %>% pull(unsolved),
  n= baltimore_summary %>% pull(n)
)

baltimore_test %>% 
  broom::tidy()
```

Problem 2

#Loading the Excel Files and creating a function for reading them
```{r}
all_files=
           list.files(path= "./long data",
                      recursive=T,
                      pattern=".csv",
                      full.names=T)

```

```{r}
reading_data= function(x){
  read=read_csv(x)
  read}
```

#Applying the function using map to create a data frame
```{r}
subject_df= 
  purrr::map_dfr(all_files,reading_data)
```
#Adding new variables for subjects, relocating them to beggining of the data frame, and changing some variables to factors
```{r}
new_df=
  subject_df %>% 
  mutate(arm= all_files) %>% 
  mutate(subject_id= all_files) %>% 
  relocate(arm) %>% 
  relocate(subject_id) %>% 
  mutate(arm= as.factor(arm))
```
#Tidying the data and separatinf variables
```{r}
tidy_data=
  pivot_longer(
    new_df, 
    week_1:week_8,
    names_to = "week", 
    names_prefix = "week_",
    values_to = "observations") %>% 
  mutate(week=as.numeric(week)) %>% 
  mutate(subject_id=as.character(subject_id)) %>% 
  mutate(arm= str_sub(arm, 13,15)) %>% 
  mutate(subject_id= str_sub(subject_id, 13,18)) 
  
view(tidy_data)
```

#Creating a spaghetti plot
```{r}
tidy_data %>% 
  ggplot(
    aes(x = week,y = observations,
        color=arm, group=subject_id))+
  geom_line()
```

#It seems like the experimental has higher observations than the control arm.

Problem 3
```{r}
library(tidyverse)
library(purrr)

set.seed(10)

iris_with_missing = iris %>% 
  map_df(~replace(.x, sample(1:150, 20), NA)) %>%
  mutate(Species = as.character(Species))
```

#Writing the function
```{r}
filling_missing_data_1= function(x){
  if (is.numeric(x)){x[is.na(x)]<-mean(x,na.rm = T)}
  if (is.character(x)){x[is.na(x)]<-"virginica"}
return(x)
  }
```
#Using map function to get a data frame
```{r}
new_iris_df= map_dfr(iris_with_missing, filling_missing_data_1)
```

```{r}
view(new_iris_df)
```



