---
title: "p8105_hw5_dr3168"
author: "Daniela Rochez"
date: "11/15/2021"
output: github_document
editor_options: 
  chunk_output_type: console
---

```{r}
library(tidyverse)
library(rvest)
```

Problem 1
#Loading CSV file
```{r}
homicide_df= 
  read_csv("homicide-data.csv", 
           na= c("", "Unknown")) %>% 
  mutate(city_state= str_c(city, state),
         resolution= case_when(
           disposition== 
             "Closed without arrest" ~ "unsolved",
           disposition== 
             "Open/No arrest" ~ "unsolved",
           disposition== 
             "Closed by arrest" ~ "solved")) %>% 
  relocate(city_state) %>% 
  filter(city_state != "TulsaAL") %>% 
  view()
```
#There are 52,169 observations. In the raw data there were some missing values however that was taken care of quickly. Key variables include city and state where the homicide took place and the age, sex and race of the victims.

#Focus on Baltimore
```{r}
baltimore_df= 
  homicide_df %>% 
  filter(city_state== "BaltimoreMD")

baltimore_summary=
  baltimore_df %>%
  summarize(unsolved= 
              sum(resolution== "unsolved"),
            n=n())

baltimore_test=
  prop.test(
  x= baltimore_summary %>% pull(unsolved),
  n= baltimore_summary %>% pull(n)
)

baltimore_test %>% 
  broom::tidy()
```

#Writing function
```{r}
prop_test_function= function (city_df){
  city_summary=
  city_df %>%
  summarize(unsolved= 
              sum(resolution== "unsolved"),
            n=n())

city_test=
  prop.test(
  x= city_summary %>% pull(unsolved),
  n= city_summary %>% pull(n)
)
  return(city_test)
}

```
#Iterating across cities
```{r}
results_df=
  homicide_df %>% 
  nest(data= uid:resolution) %>% 
  mutate(test_results= 
           map(data,prop_test_function),
         tidy_results=
           map(test_results,broom::tidy)) %>% 
  select(city_state, tidy_results) %>% 
  unnest(tidy_results) %>% 
  select(city_state, estimate, starts_with("conf"))

```
#Making a plot showing estimates and CIs
```{r}
results_df %>%
  mutate(city_state= fct_reorder(city_state, estimate)) %>% 
  ggplot(aes(x=city_state, y=estimate)) +
  geom_point() +
  geom_errorbar(aes(ymin= conf.low, ymax= conf.high))+
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))
```

Problem 2

#Loading the Excel Files and creating a function for reading them
```{r}
all_files=
           list.files(path= "./long data",
                      recursive=T,
                      pattern=".csv",
                      full.names=T)
```

```{r}
reading_data= function(x){
  read=read_csv(x)
  read}
```

#Applying the function using map to create a data frame
```{r}
subject_df= 
  purrr::map_dfr(all_files,reading_data)
```
#Adding new variables for subjects, relocating them to beggining of the data frame, and changing some variables to factors
```{r}
new_df=
  subject_df %>% 
  mutate(arm= all_files) %>% 
  mutate(subject_id= all_files) %>% 
  relocate(arm) %>% 
  relocate(subject_id) %>% 
  mutate(arm= as.factor(arm))
```
#Tidying the data and separatinf variables
```{r}
tidy_data=
  pivot_longer(
    new_df, 
    week_1:week_8,
    names_to = "week", 
    names_prefix = "week_",
    values_to = "observations") %>% 
  mutate(week=as.numeric(week)) %>% 
  mutate(subject_id=as.character(subject_id)) %>% 
  mutate(arm= str_sub(arm, 13,15)) %>% 
  mutate(subject_id= str_sub(subject_id, 13,18)) 
  
view(tidy_data)
```

#Creating a spaghetti plot
```{r}
tidy_data %>% 
  ggplot(
    aes(x = week,y = observations,
        color=arm, group=subject_id))+
  geom_line()
```

#It seems like the experimental has higher observations than the control arm.

Problem 3
```{r}
library(tidyverse)
library(purrr)

set.seed(10)

iris_with_missing = iris %>% 
  map_df(~replace(.x, sample(1:150, 20), NA)) %>%
  mutate(Species = as.character(Species))
```

#Writing the function
```{r}
filling_missing_data_1= function(x){
  if (is.numeric(x)){x[is.na(x)]<-mean(x,na.rm = T)}
  if (is.character(x)){x[is.na(x)]<-"virginica"}
return(x)
  }
```
#Using map function to get a data frame with no missinf values
```{r}
new_iris_df= map_dfr(iris_with_missing, filling_missing_data_1)
view(new_iris_df)
```



